---
title: "Household Level File"
author: "Carlee Griffeth"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries, message=FALSE}
library(tidyverse)
library(survey)
library(srvyr)
library(treemapify)
library(knitr)
library(jtools)
library(qqman)
library(ggplot2)
library(hrbrthemes)
library(tidyverse)
library(survey)
library(srvyr)
library(treemapify)
library(knitr)
library(jtools)
library(interactions)
```

# Setting Up

```{r loading dataset}
read_csv("NHTS_data/vehpub.csv")
read_csv("NHTS_data/perpub.csv")
read_csv("NHTS_data/hhpub.csv")
```

# Loading NHTS Data

## Household file

HOUSEID: Household Identifier
HHVEHCNT: Count of Household vehicles
HHSTATE: Household state
HHFAMINC: Household income
HOMEOWN: Home Ownership

RAIL: MSA heavy rail status for household (current transit access)
WALK: Frequency of Walking for Travel (walkability)
TRAIN: Frequency of Train Use for Travel (proxy for quality of current transit service)
HBHUR: Urban / Rural indicator - Block group (where transit isn't but could be)
  • Urban: areas with population density scores (based on density
          centiles) mostly between 75 and 99. They include both the downtowns of major cities
          and surrounding neighborhoods. Households within this classification live within the
          classic high-density neighborhoods found in the heart of America’s largest cities. While
          almost always anchored by the downtown central business district, these areas often
          extend beyond city limits and into surrounding jurisdictions to encompass most of
          America’s earliest suburban expansions.
  • Second City: are  areas less-densely populated than urban areas,
          with population density scores typically between 40 and 90. While similar to suburban
          areas in their densities, second cities are the population centers of their surrounding
          communities. As such, many are concentrated within America’s larger towns and
          smaller cities. This class also includes thousands of satellite cities, which are
          higher-density suburbs encircling major metropolitan centers, typically with far greater
          affluence than their small city cousins.
  • Suburban: areas with population density scores between 40 and 90,
          and are tied closely to urban areas or second cities. Unlike second cities (defined
          below), suburban areas are not the population center of their surrounding community,
          but rather a continuation of the density decline from the city center. While some suburbs
          may be employment centers, their lifestyles and commuting patterns will be more tied to
          one another, or to the urban or second city core, than within themselves.
  • Small Town & Rural: contain households that are classified with one of those two
          urbanicity classifications. The population density scores where they are found range
          from 0 to 40. This category includes exurbs, towns, farming communities, and a wide
          range of other rural areas. The town aspect of this class covers the thousands of small
          towns and villages scattered throughout the rural heartland, as well as the low-density
          areas far beyond the outer beltways and suburban rings of America’s major metros.
          Households in the exurban segments have slightly higher densities and are more
          affluent than their rural neighbors.
      https://nhts.ornl.gov/assets/Assessing_the_Role_of_Urbanicity.pdf

```{r load hh data, message=FALSE}
hhs <- read_csv("NHTS_data/hhpub.csv") %>%
  select(HOUSEID, HHVEHCNT, HHSTATE, HHFAMINC, HOMEOWN, RAIL, WALK, TRAIN, HBHUR, WTHHFIN) %>%
  mutate(has_veh = HHVEHCNT > 0) %>%
  mutate(income_k = case_when(HHFAMINC == "01" ~ 5,
                              HHFAMINC == "02" ~ 12.5,
                              HHFAMINC == "03" ~ 20,
                              HHFAMINC == "04" ~ 30,
                              HHFAMINC == "05" ~ 42.5,
                              HHFAMINC == "06" ~ 62.5,
                              HHFAMINC == "07" ~ 87.5,
                              HHFAMINC == "08" ~ 112.5,
                              HHFAMINC == "09" ~ 137.5,
                              HHFAMINC == "10" ~ 175,
                              HHFAMINC == "11" ~ 250,
                              TRUE ~ -1)) %>%
  mutate(homeown = case_when(HOMEOWN == "01" ~ "Own",
                             HOMEOWN == "02" ~ "Rent",
                             TRUE ~ "zOther")) %>%
  mutate(rail_access = case_when(RAIL == "01" ~ "Has Rail",
                          RAIL == "02" ~ "No Rail",
                          TRUE ~ "zOther")) %>%
  mutate(walks = case_when(WALK == "01" ~ "Always Walks",
                             WALK == "02" ~ "Sometimes Walks",
                             WALK == "03" ~ "Sometimes Walks",
                             WALK == "04" ~ "Sometimes Walks",
                             WALK == "05" ~ "Never Walk",
                             TRUE ~ "zOther")) %>%
  mutate(trains = case_when(TRAIN == "01" ~ "Always Trains",
                             TRAIN == "02" ~ "Sometimes Trains",
                             TRAIN == "03" ~ "Sometimes Trains",
                             TRAIN == "04" ~ "Sometimes Trains",
                             TRAIN == "05" ~ "Never Walk",
                             TRUE ~ "zOther")) %>%
  mutate(density = case_when(HBHUR == "C" ~ "Second City",
                             HBHUR == "R" ~ "Rural",
                             HBHUR == "S" ~ "Suburban",
                             HBHUR == "T" ~ "Small Town",
                             HBHUR == "U" ~ "Urban",
                             TRUE ~ "zOther")) %>%
  select(HOUSEID, has_veh, HHSTATE, income_k, homeown, rail_access, walks, trains, density, WTHHFIN)
```

## Vehicle File

HOUSEID: Household Identifier
HFUEL: Type of Hybrid Vehicle (03 = EV)

```{r load vehicle data, message=FALSE}
vehs <- read_csv("NHTS_data/vehpub.csv") %>%
  select(HOUSEID, HH_HISP, HH_RACE, FUELTYPE, HFUEL, WTHHFIN) %>%
  mutate(race_eth = factor(case_when(HH_HISP == "01" ~ "Hispanic",
                              HH_RACE == "01" ~ "NH_white",
                              HH_RACE == "02" ~ "NH_Black",
                              HH_RACE == "03" ~ "NH_Asian",
                              TRUE ~ "Other"),
                           levels = c("NH_white",
                                      "NH_Black",
                                      "NH_Asian",
                                      "Hispanic",
                                      "Other"))) %>%
  mutate(type = case_when(FUELTYPE == "01" ~ "Gas",
                          FUELTYPE == "02" ~ "Diesel",
                          HFUEL == "01" ~ "Biodiesel",
                          HFUEL == "02" ~ "Plug-in hybrid",
                          HFUEL == "03" ~ "Fully electric",
                          HFUEL == "04" ~ "Hybrid",
                          TRUE ~ "Other")) %>%
  mutate(is_ev = HFUEL == "03") %>%
  group_by(HOUSEID) %>%
  summarize(has_ev = max(is_ev))
```

### Merge Veh into HH

```{r}
hhs <- hhs %>%
  left_join(vehs)
```

## Person File 

HOUSEID: Household Identifier
R_RACE: Respondent Race (01 = white)
R_HISP: No, Not Hispanic or Latino
CONDPUB: Medical Condition Results in Using Bus or Subway Less Frequently

```{r load person data, message=FALSE}
ppl <- read_csv("NHTS_data/perpub.csv") %>%
  select(HOUSEID, R_RACE, R_HISP, WRKTRANS, WRK_HOME, NOCONG, TIMETOWK, WTPERFIN) %>%
  mutate(is_nh_white = (R_RACE == "01" & R_HISP == "02")) %>%
  mutate(modeshare = case_when(WRKTRANS == "01" ~ "Walk",
                              WRKTRANS == "02" ~ "Bike",
                              WRKTRANS == "03" ~ "Car",
                              WRKTRANS == "04" ~ "SUV",
                              WRKTRANS == "05" ~ "Van",
                              WRKTRANS == "06" ~ "Pickup Truck",
                              WRKTRANS == "07" ~ "Golfcart / Segway",
                              WRKTRANS == "08" ~ "Motorcycle / Moped",
                              WRKTRANS == "09" ~ "RV, motor home, ATV, snowmobile",
                              WRKTRANS == "10" ~ "School bus",
                              WRKTRANS == "11" ~ "Public or commuter bus",
                              WRKTRANS == "12" ~ "Paratransit / Dial-a-ride",
                              WRKTRANS == "13" ~ "Private / Charter / Tour / Shuttle bus",
                              WRKTRANS == "14" ~ "City-to-city bus (Greyhound, Megabus)",
                              WRKTRANS == "15" ~ "Amtrak / Commuter rail",
                              WRKTRANS == "16" ~ "Subway / Elevated / Light rail / Street car",
                              WRKTRANS == "17" ~ "Taxi / Limo (including Uber / Lyft)",
                              WRKTRANS == "18" ~ "Rental car (including Zipcar / Car2Go)",
                              WRKTRANS == "19" ~ "Airplane",
                              WRKTRANS == "20" ~ "Boat / Ferry / Water taxi",
                              TRUE ~ "Other")) %>%
  mutate(pubtransit = case_when(WRKTRANS == "11" ~ "Public Transit",
                               WRKTRANS == "16" ~ "Public Transit",
                               WRKTRANS == "20" ~ "Public Transit",
                               TRUE ~ "Not Public Transit")) %>%
  mutate(wfh = case_when(WRK_HOME == "01" ~ "Yes",
                         WRK_HOME == "02" ~ "No",
                         TRUE ~ "Other")) %>%
select(HOUSEID, modeshare, is_nh_white, pubtransit, wfh) %>%
group_by(HOUSEID)

bipoc <- ppl %>%
  summarize(has_BIPOC = !as.logical(min(is_nh_white))) 
```

### Merge Person into HH

```{r}
hhs <- hhs %>%
  left_join(ppl)

hhs <- hhs %>%
  left_join(bipoc)
```

## Applying Survey Weights

```{r Create survey}
hhs_svy <- hhs %>%
  as_survey(HOUSEID, weight = WTHHFIN)
```

# Descriptive Statistics

## Car Type

### Car Type Table

```{r ev shares}
ev_shares_list <- svytable(~type, hhs_svy)

ev_shares_tibble <- tibble(`Type of vehicle` = 
                             factor(names(ev_shares_list),
                                    levels = c("Gas",
                                               "Diesel",
                                               "Biodiesel",
                                               "Hybrid",
                                               "Plug-in hybrid",
                                               "Fully electric",
                                               "Other")), 
                           `Number of vehicles` = as.numeric(round(ev_shares_list,0)),
                           `Percent of total` = paste(round((ev_shares_list / sum(ev_shares_list)) * 100, 2), "%", sep = "")) %>%
 
   arrange(`Type of vehicle`)

  kable(ev_shares_tibble, 
       format.args = list(big.mark = ","),
       align = "lrc")

```

### Car Type GGPlot

```{r}
ggplot(ev_shares_tibble, aes(area = `Number of vehicles`, 
                             fill = `Type of vehicle`)) +
  
  geom_treemap(color = "transparent") +
  
  scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "gray55",
                               "#9c406d",
                               "#a19f9c",
                               "#dac17b",
                               "#B9CAC4"))

```

#### Save Car Type GGPlot

```{r}
ggsave(
  filename = "vehicle type.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```
## Income 

### Income Table

```{r, warning=FALSE}
income_summary <- hhs_svy %>%
  group_by(type) %>%
  summarize(mean_inc = survey_mean(income_k),
            med_inc = survey_quantile(income_k, 0.5)) %>%
  mutate(type = factor(type, levels = c("Gas",
                                        "Diesel",
                                        "Biodiesel",
                                        "Hybrid",
                                        "Plug-in hybrid",
                                        "Fully electric",
                                        "Other"))) %>%
  arrange(type)

colnames(income_summary) <- c("Type of vehicle",
                    "Average owner's household income (thousands)",
                    "Standard error of average",
                    "Median owner's household income (thousands)",
                    "Standard error of median")

kable(income_summary, align = "lrrrr", digits = 1)
```

### Income ggplot

```{r}
ggplot(income_summary, aes(x = `Type of vehicle`,
      y = `Average owner's household income (thousands)`,
      fill = `Type of vehicle`)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "#B9CAC4",
                               "#9c406d",
                               "#D69AB7",
                               "#dac17b",
                               "gray55")) +
  theme_bw() +
  theme(legend.position = "none")

```

#### Save Income ggplot

```{r}
ggsave(
  filename = "income.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```

## Race

### Race by Type Table

```{r, warning=FALSE}
race_shares_list <- svytable(~race_eth+type, hhs_svy)

race_shares_tibble <- tibble(
  `Race/ethnicity` = factor(c(names(race_shares_list[,1]), "Total"),
                       levels = c("NH_white",
                                  "NH_Black",
                                  "NH_Asian",
                                  "Hispanic",
                                  "Other",
                                  "Total")), 
   Gas = c(round((race_shares_list[,"Gas"] / 
                              sum(race_shares_list[,"Gas"])) * 
                   100, 2), 100),
   Diesel = c(round((race_shares_list[,"Diesel"] / 
                        sum(race_shares_list[,"Diesel"])) * 
                      100, 2), 100),
   Biodiesel = c(round((race_shares_list[,"Biodiesel"] / 
                        sum(race_shares_list[,"Biodiesel"])) * 
                         100, 2), 100),
   Hybrid = c(round((race_shares_list[,"Hybrid"] / 
                        sum(race_shares_list[,"Hybrid"])) * 
                      100, 2), 100),
  `Plug-in hybrid` = c(round((race_shares_list[,"Plug-in hybrid"] / 
                          sum(race_shares_list[,"Plug-in hybrid"])) *
                            100, 2), 100),
  `Fully electric` = c(round((race_shares_list[,"Fully electric"] / 
                          sum(race_shares_list[,"Fully electric"])) *
                            100, 2), 100),
   Other = c(round((race_shares_list[,"Other"] / 
                          sum(race_shares_list[,"Other"])) *
                            100, 2), 100)) %>%
  arrange(`Race/ethnicity`)

kable(race_shares_tibble, digits = 1,
      caption = "Percent of vehicles owned, by race and type")
```

### Race by Type ggplot

```{r}
race_shares_tibble %>%
  filter(`Race/ethnicity` != "Total") %>%
  pivot_longer(cols = -`Race/ethnicity`, 
               names_to = "Type", values_to = "Share") %>%
  mutate(Type = factor(Type, levels = c("Gas",
                                        "Diesel",
                                        "Biodiesel",
                                        "Hybrid",
                                        "Plug-in hybrid",
                                        "Fully electric",
                                        "Other"))) %>%
  ggplot(aes(x = `Type`, y = Share, fill = `Race/ethnicity`)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_brewer(type = "qual", 
                    labels = c("Non-Hispanic white",
                               "Non-Hispanic Black",
                               "Non-Hispanic Asian",
                               "Hispanic",
                               "Other")) +
    scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "#B9CAC4",
                               "#9c406d",
                               "#D69AB7",
                               "#dac17b",
                               "gray55")) +
  scale_y_continuous(name = 
            "Percent of vehicles by household race/ethnicity",
            breaks = breaks <- seq(0, 100, by = 10),
            labels = paste(breaks, "%", sep = ""))
```

#### Save Race by Type ggplot

```{r}
ggsave(
  filename = "race by type.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```

### Car Type by Race Table

```{r, warning=FALSE}
race_shares_tibble2 <- tibble(
  `Vehicle type` = factor(c(names(race_shares_list[1,]), "Total"),
                          levels = c("Gas",
                                     "Diesel",
                                     "Biodiesel",
                                     "Hybrid",
                                     "Plug-in hybrid",
                                     "Fully electric",
                                     "Other",
                                     "Total")), 
  `Non-Hispanic white` = c(round((race_shares_list["NH_white",] / 
                        sum(race_shares_list["NH_white",])) * 
                          100, 2), 100), 
  `Non-Hispanic Black` = c(round((race_shares_list["NH_Black",] / 
                        sum(race_shares_list["NH_Black",])) * 
                          100, 2), 100),
  `Non-Hispanic Asian` = c(round((race_shares_list["NH_Asian",] / 
                        sum(race_shares_list["NH_Asian",])) * 
                          100, 2), 100),
  Hispanic = c(round((race_shares_list["Hispanic",] / 
                        sum(race_shares_list["Hispanic",])) * 
                       100, 2), 100),
   Other = c(round((race_shares_list["Other",] / 
                        sum(race_shares_list["Other",])) * 
                     100, 2), 100)) %>%
  arrange(`Vehicle type`)

kable(race_shares_tibble2, digits = 1,
      caption = "Percent of vehicles owned, by type and race")
```

### Car Type by Race ggplot

```{r}
race_shares_tibble2 %>%
  filter(`Vehicle type` != "Total" &
           `Vehicle type` != "Gas") %>%
  pivot_longer(cols = -`Vehicle type`, 
               names_to = "Race/ethnicity", values_to = "Share") %>%
  mutate(`Race/ethnicity` = factor(`Race/ethnicity`, 
                                   levels = c("Non-Hispanic white",
                                              "Non-Hispanic Black",
                                              "Non-Hispanic Asian",
                                              "Hispanic",
                                              "Other"))) %>%
  ggplot(aes(x = `Race/ethnicity`, y = Share, fill = `Vehicle type`)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "#B9CAC4",
                               "#9c406d",
                               "#D69AB7",
                               "#dac17b",
                               "gray55")) +
  scale_y_continuous(name = 
"Percent of vehicles by vehicle type\n(gas-powered vehicles not shown)",
            breaks = breaks <- seq(0, 6, by = 0.5),
            labels = paste(breaks, "%", sep = "")) +
  scale_x_discrete(labels = c("Non-Hispanic\nwhite",
                              "Non-Hispanic\nBlack",
                              "Non-Hispanic\nAsian",
                              "Hispanic",
                              "Other"))
```

#### Save Car Type by Race ggplot

```{r}
ggsave(
  filename = "type by race.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```
## Rail Access 

### Rail Access Table

```{r, warning=FALSE}
rail_list <- svytable(~rail_access+type, hhs_svy)

rail_tibble <- tibble(
  `Rail Access` = factor(c(names(rail_list[,1]), "Total"),
                       levels = c("Has Rail",
                                  "No Rail",
                                  "zOther",
                                  "Total")), 
   Gas = c(round((rail_list[,"Gas"] / 
                              sum(rail_list[,"Gas"])) * 
                   100, 2), 100),
   Diesel = c(round((rail_list[,"Diesel"] / 
                        sum(rail_list[,"Diesel"])) * 
                      100, 2), 100),
   Biodiesel = c(round((rail_list[,"Biodiesel"] / 
                        sum(rail_list[,"Biodiesel"])) * 
                         100, 2), 100),
   Hybrid = c(round((rail_list[,"Hybrid"] / 
                        sum(rail_list[,"Hybrid"])) * 
                      100, 2), 100),
  `Plug-in hybrid` = c(round((rail_list[,"Plug-in hybrid"] / 
                          sum(rail_list[,"Plug-in hybrid"])) *
                            100, 2), 100),
  `Fully electric` = c(round((rail_list[,"Fully electric"] / 
                          sum(rail_list[,"Fully electric"])) *
                            100, 2), 100),
   Other = c(round((rail_list[,"Other"] / 
                          sum(rail_list[,"Other"])) *
                            100, 2), 100)) %>%
  arrange(`Rail Access`)

kable(rail_tibble, digits = 1,
      caption = "Percent of vehicles owned, by density")
```

## Walks 

### Walks Table

```{r, warning=FALSE}
walks_list <- svytable(~walks+type, hhs_svy)

walks_tibble <- tibble(
  `Walks` = factor(c(names(walks_list[,1]), "Total"),
                       levels = c("Always Walks",
                             "Sometimes Walks",
                             "Never Walk",
                                  "zOther",
                                  "Total")), 
   Gas = c(round((walks_list[,"Gas"] / 
                              sum(walks_list[,"Gas"])) * 
                   100, 2), 100),
   Diesel = c(round((walks_list[,"Diesel"] / 
                        sum(walks_list[,"Diesel"])) * 
                      100, 2), 100),
   Biodiesel = c(round((walks_list[,"Biodiesel"] / 
                        sum(walks_list[,"Biodiesel"])) * 
                         100, 2), 100),
   Hybrid = c(round((walks_list[,"Hybrid"] / 
                        sum(walks_list[,"Hybrid"])) * 
                      100, 2), 100),
  `Plug-in hybrid` = c(round((walks_list[,"Plug-in hybrid"] / 
                          sum(walks_list[,"Plug-in hybrid"])) *
                            100, 2), 100),
  `Fully electric` = c(round((walks_list[,"Fully electric"] / 
                          sum(walks_list[,"Fully electric"])) *
                            100, 2), 100),
   Other = c(round((walks_list[,"Other"] / 
                          sum(walks_list[,"Other"])) *
                            100, 2), 100)) %>%
  arrange(`Walks`)

kable(walks_tibble, digits = 1,
      caption = "Percent of vehicles owned, by density")
```

## Trains

### Trains Table

```{r, warning=FALSE}
trains_list <- svytable(~trains+type, hhs_svy)

trains_tibble <- tibble(
  `Trains` = factor(c(names(trains_list[,1]), "Total"),
                       levels = c("Always Trains",
                             "Sometimes Trains",
                             "Never Walk",
                                  "zOther",
                                  "Total")), 
   Gas = c(round((trains_list[,"Gas"] / 
                              sum(trains_list[,"Gas"])) * 
                   100, 2), 100),
   Diesel = c(round((trains_list[,"Diesel"] / 
                        sum(trains_list[,"Diesel"])) * 
                      100, 2), 100),
   Biodiesel = c(round((trains_list[,"Biodiesel"] / 
                        sum(trains_list[,"Biodiesel"])) * 
                         100, 2), 100),
   Hybrid = c(round((trains_list[,"Hybrid"] / 
                        sum(trains_list[,"Hybrid"])) * 
                      100, 2), 100),
  `Plug-in hybrid` = c(round((trains_list[,"Plug-in hybrid"] / 
                          sum(trains_list[,"Plug-in hybrid"])) *
                            100, 2), 100),
  `Fully electric` = c(round((trains_list[,"Fully electric"] / 
                          sum(trains_list[,"Fully electric"])) *
                            100, 2), 100),
   Other = c(round((trains_list[,"Other"] / 
                          sum(trains_list[,"Other"])) *
                            100, 2), 100)) %>%
  arrange(`Trains`)

kable(trains_tibble, digits = 1,
      caption = "Percent of vehicles owned, by density")
```

## Density

### Density by Type Table

```{r, warning=FALSE}
density_list <- svytable(~hhdensity+type, hhs_svy)

density_tibble <- tibble(
  `Density` = factor(c(names(density_list[,1]), "Total"),
                       levels = c("Second City",
                                  "Rural",
                                  "Suburban",
                                  "Small Town",
                                  "Urban",
                                  "Other",
                                  "Total")), 
   Gas = c(round((density_list[,"Gas"] / 
                              sum(density_list[,"Gas"])) * 
                   100, 2), 100),
   Diesel = c(round((density_list[,"Diesel"] / 
                        sum(density_list[,"Diesel"])) * 
                      100, 2), 100),
   Biodiesel = c(round((density_list[,"Biodiesel"] / 
                        sum(density_list[,"Biodiesel"])) * 
                         100, 2), 100),
   Hybrid = c(round((density_list[,"Hybrid"] / 
                        sum(density_list[,"Hybrid"])) * 
                      100, 2), 100),
  `Plug-in hybrid` = c(round((density_list[,"Plug-in hybrid"] / 
                          sum(density_list[,"Plug-in hybrid"])) *
                            100, 2), 100),
  `Fully electric` = c(round((density_list[,"Fully electric"] / 
                          sum(density_list[,"Fully electric"])) *
                            100, 2), 100),
   Other = c(round((density_list[,"Other"] / 
                          sum(density_list[,"Other"])) *
                            100, 2), 100)) %>%
  arrange(`Density`)

kable(density_tibble, digits = 1,
      caption = "Percent of vehicles owned, by density")
```

### Density by Type ggplot

```{r}
density_tibble %>%
  filter(`Density` != "Total") %>%
  pivot_longer(cols = -`Density`, 
               names_to = "Type", values_to = "Share") %>%
  mutate(Type = factor(Type, levels = c("Gas",
                                        "Diesel",
                                        "Biodiesel",
                                        "Hybrid",
                                        "Plug-in hybrid",
                                        "Fully electric",
                                        "Other"))) %>%
  ggplot(aes(x = `Type`, y = Share, fill = `Density`)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_brewer(type = "qual", 
                    labels = c("Second City",
                                  "Rural",
                                  "Suburban",
                                  "Small Town",
                                  "Urban",
                                  "Other",
                                  "Total")) +
    scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "#B9CAC4",
                               "#9c406d",
                               "#D69AB7",
                               "#dac17b",
                               "gray55")) +
  scale_y_continuous(name = 
            "Percent of vehicles by density",
            breaks = breaks <- seq(0, 100, by = 10),
            labels = paste(breaks, "%", sep = ""))
```

#### Save Density by Type ggplot

```{r}
ggsave(
  filename = "density by type.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```

### Car Type by Density Table

```{r, warning=FALSE}
density_tibble2 <- tibble(
  `Vehicle type` = factor(c(names(density_list[1,]), "Total"),
                          levels = c("Gas",
                                     "Diesel",
                                     "Biodiesel",
                                     "Hybrid",
                                     "Plug-in hybrid",
                                     "Fully electric",
                                     "Other",
                                     "Total")), 
  `Second City` = c(round((density_list["Second City",] / 
                        sum(density_list["Second City",])) * 
                          100, 2), 100), 
  `Rural` = c(round((density_list["Rural",] / 
                        sum(density_list["Rural",])) * 
                          100, 2), 100),
  `Suburban` = c(round((density_list["Suburban",] / 
                        sum(density_list["Suburban",])) * 
                          100, 2), 100),
  `Small Town` = c(round((density_list["Small Town",] / 
                        sum(density_list["Small Town",])) * 
                       100, 2), 100),
  `Urban` = c(round((density_list["Urban",] / 
                        sum(density_list["Urban",])) * 
                       100, 2), 100),
   Other = c(round((density_list["Other",] / 
                        sum(density_list["Other",])) * 
                     100, 2), 100)) %>%
  arrange(`Vehicle type`)

kable(density_tibble2, digits = 1,
      caption = "Percent of vehicles owned, by type and race")
```

### Car Type by Density ggplot

```{r}
density_tibble2 %>%
  filter(`Vehicle type` != "Total" &
           `Vehicle type` != "Gas") %>%
  pivot_longer(cols = -`Vehicle type`, 
               names_to = "Density", values_to = "Share") %>%
  mutate(`Density` = factor(`Density`, 
                                   levels = c("Second City",
                                  "Rural",
                                  "Suburban",
                                  "Small Town",
                                  "Urban",
                                  "Other",
                                  "Total"))) %>%
  ggplot(aes(x = `Density`, y = Share, fill = `Vehicle type`)) +
  geom_bar(stat = "identity") +
  theme_bw() +
  scale_fill_manual(values = c("#303f39",
                               "#559274",
                               "#B9CAC4",
                               "#9c406d",
                               "#D69AB7",
                               "#dac17b",
                               "gray55")) +
  scale_y_continuous(name = 
"Percent of vehicles by vehicle type\n(gas-powered vehicles not shown)",
            breaks = breaks <- seq(0, 6, by = 0.5),
            labels = paste(breaks, "%", sep = "")) +
  scale_x_discrete(labels = c("Second City",
                                  "Rural",
                                  "Suburban",
                                  "Small Town",
                                  "Urban",
                                  "Other",
                                  "Total"))
```

#### Save Car Type by Density ggplot

```{r}
ggsave(
  filename = "type by density.png",
  plot = last_plot(),
  device = "png",
  path = "/Users/carleegriffeth/Documents/Thesis/07 Graphics/ggplots",
  scale = 1,
  width = par("din")[1], 
  height = par("din")[2], 
  units = c("in", "cm","mm"),
  dpi = 320,
  limitsize = TRUE,
)
```

# Regression

```{r three-IV regression}
model1 <- glm(has_ev ~ income_k + has_BIPOC + rail_access + walks + trains + density, 
              data = hhs, 
              family = "binomial")

summary(model1)
```

```{r three-IV regression}
model2 <- glm(has_ev ~ log(income_k) + has_BIPOC + rail_access + walks + trains + density, 
              data = hhs, 
              family = "binomial")

summary(model2)
```

```{r three-IV regression}
model3 <- glm(has_ev ~ log(income_k) + has_BIPOC + rail_access + walks + trains + density +
                log(income_k):has_BIPOC,
              data = hhs, 
              family = "binomial")

summary(model3)
```

## Result Table

```{r results summary}
coef_names <- c("Income (thousands)" = "income_k",
                "Income (log-transformed)" = "log(income_k)", 
                "Presence of BIPOC in household" = "has_BIPOCTRUE",
                "rail_accessNo Rail" = "rail_accessNo Rail",
                "walksNever Walk" = "walksNever Walk",
                "walksSometimes Walk" = "walksSometimes Walks",
                "walksOther Walk" = "walkszOther",
                "trainsNever Trains" = "trainsNever Walk",
                "trainsSometimes Trains" = "trainsSometimes Trains",
                "trainsOther Trains" = "trainszOther",
                "Second City" = "densitySecond City",
                "Small Town" = "densitySmall Town",
                "Suburban" = "densitySuburban",
                "Urban" = "densityUrban",
                "Density Other" = "densityzOther",
                "Interact: Income and BIPOC" = "log(income_k):has_BIPOCTRUE",
                "Constant" = "(Intercept)")

export_summs(model1, model2, model3, coefs = coef_names)
```
