---
title: "R2_Tract_Regression"
author: "Carlee Griffeth"
date: "2/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up

## Loading Libraries

*Note: there may be unecessaary libraries in this list; this has become a running list of libraries I've added to try different functions that I've found online so some may not actually be needed.

```{r load libraries, message=FALSE}
library(tidyverse)
library(tidycensus)
library(purrr)
library(survey)
library(srvyr)
library(knitr)
library(jtools)
library(sf)
library(sp)
library(units)
library(nngeo)
library(leaflet)
library(tigris)
library(reshape2)
library(httr)
library(jsonlite)
library(rgdal)
library(maps)
library(mapdata)
library(dplyr)
library(ggplot2)
library(cartogram)
library(ggspatial)
library(ggthemes)
library(rnaturalearth)
library("ggthemes")
library("mapproj")
library("ggspatial")

census_api_key("84fd7c10ce8fd8c15d8852fd68abaa8790f1c29d")
options(tigris_use_cache = TRUE)
```

# Loading & Cleaning Data

## EVCS Dataset

Manually downaloaded and read into r.

Electric vehicle charging station data is pulled from the US Department of Energy Alternative Fuels Data Center's Alternative Fueling Station Locator at https://afdc.energy.gov/stations/#/analyze?country=US&fuel=ELEC&ev_levels=all&access=public&access=private

Filtered for download by:
1. Location: United States -- all states/territories
2. Fuel: Electric -- all charger types, all connectors, all networks selected
3. Station: 
    - public and private access; 
    - status: available; 
    - owner: all; 
    - payment: all

```{r loading datasets}
evcs <- read_csv("Station_Data/evcs.csv") %>%
                  select(Station_Name, Street_Address, City, StateAbb, ZIP, 
                         Access_Days_Time, EV_Network, Latitude, Longitude, 
                         Owner_Type_Code, Access_Code, EV_Pricing, EV_Connector) %>%
                  mutate(access_time = case_when(Access_Days_Time == "24 hours daily" ~ "24 hours daily",
                                            Access_Days_Time == "24 hours" ~ "24 hours",
                                            Access_Days_Time == "MON: 24 hours | TUE: 24 hours | WED: 24 hours | THU: 24 hours | FRI: 24 hours | SAT: 24 hours | SUN: 24 hours" ~ "24 hours daily", 
                                            Access_Days_Time == "MO: 12:00am-12:00am; TU: 12:00am-12:00am; WE: 12:00am-12:00am; TH: 12:00am-12:00am; FR: 12:00am-12:00am; SA: 12:00am-12:00am; SU: 12:00am-12:00am" ~ "24 hours daily",
                                            TRUE ~ "Not 24 hours daily")) %>%
                  mutate(ownership = case_when(Owner_Type_Code == "FG" ~ "Federal Government",
                                               Owner_Type_Code == "J" ~ "Joint",
                                               Owner_Type_Code == "LG" ~ "Local Government",
                                               Owner_Type_Code == "P" ~ "Private",
                                               Owner_Type_Code == "SG" ~ "State Government",
                                               Owner_Type_Code == "T" ~ "Utility",
                                               TRUE ~ "Blank",
                                               FALSE ~ "None")) %>%
                  mutate(access_type = case_when(Access_Code == "public" ~ "Public Accessiblity",
                                               Access_Code == "private" ~ "Private Accessibility",
                                               TRUE ~ "Blank",
                                               FALSE ~ "None")) %>%
                  mutate(freepay = case_when(EV_Pricing == "Free" ~ "Free",
                                             EV_Pricing == "FREE" ~ "Free",
                                             TRUE ~ "Pay",
                                             FALSE ~ "Pay")) %>%
select(Station_Name, Street_Address, City, StateAbb, ZIP, access_time, EV_Network, Latitude, Longitude, ownership, access_type, freepay, EV_Connector)

free_evcs <- filter(evcs, access_time != "Not 24 hours daily" & access_type == "Public Accessiblity" & freepay != "Pay" & EV_Network != "Tesla Destination" & EV_Connector != "TESLA")
```

## Census Data

Pulling All Tracts

NOTE: 'ALAND' variable in "us_shape" is in square meters. 

tract polygons projected in: NAD83

```{r}
#Loading the list of ACS variables just to have on hand for reference. 
#v17 <- load_variables(2017, "acs5", cache = TRUE)

us <- unique(fips_codes$state)[1:51]

us_shape <- map_df(us, function(x) {
                  tracts(state = x, 
                            cb = FALSE, 
                          year = 2017)})
```

### Selecting Census Variables 

  B01003_001 = total population
  B25001_001 = total housing units
  B25003_001 = total occupied housing units
  B25003_002 = total owner occupied housing units
  B25003_003 = total renter  occupied housing units
  B03002_003 = Not Hispanic or Latino!!White alone
  B03002_004 = Not Hispanic or Latino!!Black or African American alone
  B03002_005 = Not Hispanic or Latino!!American Indian and Alaska Native alone
  B03002_006 = Not Hispanic or Latino!!Asian alone
  B03002_007 = Not Hispanic or Latino!!Native Hawaiian and Other Pacific Islander alone
  B03002_012 = Hispanic or Latino
  B08301_001 = Means to work: Total
  B08301_003 = Means to work: Car truck or van!!Drove alone
  B08301_010 = Means to work: Public transportation (excluding taxicab)
  B08301_021 = Worked at home
  B19013_001 = Median household income in the past 12 months (in 2017 inflation-adjusted dollars)

```{r selecting census variables}
acs_data <- map_df(us, function(x) {
                  get_acs(geography ="tract",
                          geometry = TRUE,
                          variables = c("B01003_001", "B25001_001", "B25003_001", "B25003_002", 
                                        "B25003_003", "B03002_003", "B03002_004", "B03002_005",
                                        "B03002_006", "B03002_007", "B03002_012", "B08301_001", 
                                        "B08301_003", "B08301_010", "B08301_021", "B19013_001"),
                          output = "wide",
                          state = x,
                          year = 2017)})

## Renaming Columns

colnames(acs_data) <- c("GEOID", "NAME", "Tot_Pop", "Tot_Pop_MOE", "Tot_HU", "Tot_HU_MOE", "Tot_HU_Occ", "Tot_HU_Occ_MOE",
                        "Tot_HU_OwnOcc", "Tot_HU_OwnOcc_MOE", "Tot_HU_RentOcc", "Tot_HU_RentOcc_MOE", "Race_WhiteNH", "Race_WhiteNH_MOE",
                        "Race_BlackNH", "Race_BlackNH_MOE", "Race_IndigenousNH", "Race_IndigenousNH_MOE", "Race_AsianNH", "Race_AsianNH_MOE", 
                        "Race_PacIslNH", "Race_PacIslNH_MOE", "Race_Hispanic", "Race_Hispanic_MOE", "Mode_Total", "Mode_Total_MOE", 
                        "Mode_CarAlone", "Mode_CarAlone_MOE", "Mode_PubTransit", "Mode_PubTransit_MOE", "Mode_WFH", "Mode_WFH_MOE", 
                        "MedInc", "MedInc_MOE", "geometry")

## Cleaning Data

acs_data <- acs_data %>%
  mutate(acs_data, percent_white = (Race_WhiteNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_black = (Race_BlackNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_indig = (Race_IndigenousNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_asian = (Race_AsianNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_pacisl = (Race_PacIslNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_hispanic = (Race_Hispanic / Tot_Pop)*100) %>%
  mutate(acs_data, percent_caralone = (Mode_CarAlone / Mode_Total)*100) %>%
  mutate(acs_data, percent_pubtransit = (Mode_PubTransit / Mode_Total)*100) %>%
  mutate(acs_data, percent_wfh = (Mode_WFH / Mode_Total)*100) %>%
  mutate(FIPS = GEOID) %>%
  mutate(states = case_when(FIPS >= "01000000000" & FIPS <= "01999999999" ~ 01,
                            FIPS >= "02000000000" & FIPS <= "02999999999" ~ 02,
                            FIPS >= "04000000000" & FIPS <= "04999999999" ~ 04,
                            FIPS >= "05000000000" & FIPS <= "05999999999" ~ 05,
                            FIPS >= "06000000000" & FIPS <= "06999999999" ~ 06,
                            FIPS >= "08000000000" & FIPS <= "08999999999" ~ 08,
                            FIPS >= "09000000000" & FIPS <= "09999999999" ~ 09,
                            FIPS >= "11000000000" & FIPS <= "11999999999" ~ 11,
                            FIPS >= "10000000000" & FIPS <= "10999999999" ~ 10,
                            FIPS >= "12000000000" & FIPS <= "12999999999" ~ 12,
                            FIPS >= "13000000000" & FIPS <= "13999999999" ~ 13,
                            FIPS >= "15000000000" & FIPS <= "15999999999" ~ 15,
                            FIPS >= "16000000000" & FIPS <= "16999999999" ~ 16,
                            FIPS >= "17000000000" & FIPS <= "17999999999" ~ 17,
                            FIPS >= "18000000000" & FIPS <= "18999999999" ~ 18,
                            FIPS >= "19000000000" & FIPS <= "19999999999" ~ 19,
                            FIPS >= "20000000000" & FIPS <= "20999999999" ~ 20,
                            FIPS >= "21000000000" & FIPS <= "21999999999" ~ 21,
                            FIPS >= "22000000000" & FIPS <= "22999999999" ~ 22,
                            FIPS >= "23000000000" & FIPS <= "23999999999" ~ 23,
                            FIPS >= "24000000000" & FIPS <= "24999999999" ~ 24,
                            FIPS >= "25000000000" & FIPS <= "25999999999" ~ 25,
                            FIPS >= "26000000000" & FIPS <= "26999999999" ~ 26,
                            FIPS >= "27000000000" & FIPS <= "27999999999" ~ 27,
                            FIPS >= "28000000000" & FIPS <= "28999999999" ~ 28,
                            FIPS >= "29000000000" & FIPS <= "29999999999" ~ 29,
                            FIPS >= "30000000000" & FIPS <= "30999999999" ~ 30,
                            FIPS >= "01000000000" & FIPS <= "31999999999" ~ 31,
                            FIPS >= "01000000000" & FIPS <= "32999999999" ~ 32,
                            FIPS >= "01000000000" & FIPS <= "33999999999" ~ 33,
                            FIPS >= "01000000000" & FIPS <= "34999999999" ~ 34,
                            FIPS >= "01000000000" & FIPS <= "35999999999" ~ 35,
                            FIPS >= "01000000000" & FIPS <= "36999999999" ~ 36,
                            FIPS >= "01000000000" & FIPS <= "37999999999" ~ 37,
                            FIPS >= "01000000000" & FIPS <= "38999999999" ~ 38,
                            FIPS >= "01000000000" & FIPS <= "39999999999" ~ 39,
                            FIPS >= "01000000000" & FIPS <= "40999999999" ~ 40,
                            FIPS >= "01000000000" & FIPS <= "41999999999" ~ 41,
                            FIPS >= "01000000000" & FIPS <= "42999999999" ~ 42,
                            FIPS >= "01000000000" & FIPS <= "44999999999" ~ 44,
                            FIPS >= "01000000000" & FIPS <= "45999999999" ~ 45,
                            FIPS >= "01000000000" & FIPS <= "46999999999" ~ 46,
                            FIPS >= "01000000000" & FIPS <= "47999999999" ~ 47,
                            FIPS >= "01000000000" & FIPS <= "48999999999" ~ 48,
                            FIPS >= "01000000000" & FIPS <= "49999999999" ~ 49,
                            FIPS >= "01000000000" & FIPS <= "50999999999" ~ 50,
                            FIPS >= "01000000000" & FIPS <= "51999999999" ~ 51,
                            FIPS >= "01000000000" & FIPS <= "53999999999" ~ 53,
                            FIPS >= "01000000000" & FIPS <= "54999999999" ~ 54,
                            FIPS >= "01000000000" & FIPS <= "55999999999" ~ 55,
                            FIPS >= "01000000000" & FIPS <= "56999999999" ~ 56,
                              TRUE ~ 0))
  
## Creating Yes/No Has EVCS Variable

poly_CRS <- st_crs(acs_data)
  points = st_as_sf(evcs, coords = c("Longitude", "Latitude"), crs = poly_CRS)
  free_points = st_as_sf(free_evcs, coords = c("Longitude", "Latitude"), crs = poly_CRS)
  
acs_data <- acs_data %>%
  mutate(num_EVCS = lengths(st_covers(acs_data, points)),
         num_free_EVCS = lengths(st_covers(acs_data, free_points))) %>%
  mutate(has_EVCS = num_EVCS > 0,
         has_free_EVCS = num_free_EVCS > 0)
```

## Political Data

Loading political variables.
Gov = political party of sitting Governor in 2017 
    - Dem, GOP, IND
StateSen = political party holding a majority in the State Senate in 2017
StateHouse = political party holding a majority in the State House in 2017
Leg = political party holding a majority in both chambers of the State Legislature in 2017
    - Dem, GOP, Split 

(note: Nebraska's state legislature is unicameral, StateSen and StateHouse are listed as 'NA'; all variables are listed as 'NA' for DC as the governance structure is not comparable to that of a state)

```{r}
poli_vars <- read_csv("Station_Data/political_var.csv") %>%
                  select(states, statename, StateAbb, Gov, StateSen, StateHouse, Leg)

## Merging Political Variables into ACS Data

acs_data <- acs_data %>%
  left_join(poli_vars)
```


## Creating Density Variable

##acs_data <- acs_data %>%
## mutate(density = sum(c(Race_BlackNH, Race_IndigenousNH, Race_AsianNH, Race_PacIslNH, Race_Hispanic)))

## Air Quality Data


# Regression

```{r three-IV regression}
model1 <- glm(has_EVCS ~ MedInc + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg,
              data = acs_data)

summary(model1)
```

## Log Income

```{r three-IV regression}
model2 <- glm(has_EVCS ~ log(MedInc) + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg,
              data = acs_data)

summary(model2)
```

## Regression with Interactions

```{r interaction regression}
model3 <- glm(has_EVCS ~ log(MedInc) + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg +
                percent_white:Gov +
                percent_white:Leg +
                log(MedInc):Gov +
                log(MedInc):Leg,
              data = acs_data)

summary(model3)
```

## Result Table

```{r results summary}
coef_names <- c("Median Income (log-transformed)" = "log(MedInc)", 
                "Percentage of Population: White (Non-Hispanic)" = "percent_white",
                "Percentage of Population: Black (Non-Hispanic)" = "percent_black",
                "Percentage of Population: Asian (Non-Hispanic)" = "percent_asian",
                "Percentage of Population: Indigenous (Non-Hispanic)" = "percent_indig",
                "Percentage of Population: Pacific Islander (Non-Hispanic)" = "percent_pacisl",
                "Percentage of Population: Hispanic" = "percent_hispanic",
                "Percentage of Workers: Drove Alone" = "percent_caralone",
                "Percentage of Workers: Public Transit" = "percent_pubtransit",
                "Percentage of Workers: Work From Home" = "percent_wfh",
                "Republican Governor" = "GovGOP",
                "Independent Governor" = "GovInd",
                "Republican Legislature" = "LegGOP",
                "Split Legislature" = "LegSplit",
                "Interaction: Percentage White and Republican Governor" = "percent_white:GovGOP",
                "Interaction: Percentage White and Independent Governor" = "percent_white:GovInd",
                "Interaction: Percentage White and Republican Legislature" = "percent_white:LegGOP",
                "Interaction: Percentage White and Split Legislature" = "percent_white:LegSplit",
                "Interaction: Median Income (log) and Republican Governor" = "log(MedInc):GovGOP",
                "Interaction: Median Income (log) and Independent Governor" = "log(MedInc):GovInd",
                "Interaction: Median Income (log) and Republican Legislature" = "log(MedInc):LegGOP",
                "Interaction: Median Income (log) and Split Legislature" = "log(MedInc):LegSplit",
                "Constant" = "(Intercept)")


export_summs(model1, model2, model3, coefs = coef_names)
```