---
title: "R3_Station_DescriptiveStats"
author: "Carlee Griffeth"
date: "2/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up

## Loading Libraries

*Note: there may be unecessaary libraries in this list; this has become a running list of libraries I've added to try different functions that I've found online so some may not actually be needed.

```{r load libraries, message=FALSE}
library(tidyverse)
library(tidycensus)
library(purrr)
library(survey)
library(srvyr)
library(knitr)
library(jtools)
library(sf)
library(sp)
library(units)
library(nngeo)
library(leaflet)
library(tigris)
library(reshape2)
library(httr)
library(jsonlite)
library(rgdal)
library(maps)
library(mapdata)
library(dplyr)
library(ggplot2)
library(cartogram)
library(ggspatial)
library(ggthemes)
library(rnaturalearth)
library("ggthemes")
library("mapproj")
library("ggspatial")

census_api_key("84fd7c10ce8fd8c15d8852fd68abaa8790f1c29d")
options(tigris_use_cache = TRUE)
```

# Loading & Cleaning Data

## EVCS Dataset

Manually downaloaded and read into r.

Electric vehicle charging station data is pulled from the US Department of Energy Alternative Fuels Data Center's Alternative Fueling Station Locator at https://afdc.energy.gov/stations/#/analyze?country=US&fuel=ELEC&ev_levels=all&access=public&access=private

Filtered for download by:
1. Location: United States -- all states/territories
2. Fuel: Electric -- all charger types, all connectors, all networks selected
3. Station: 
    - public and private access; 
    - status: available; 
    - owner: all; 
    - payment: all

```{r loading datasets}
evcs <- read_csv("Station_Data/evcs.csv") %>%
                  select(Station_Name, Street_Address, City, StateAbb, ZIP, 
                         Access_Days_Time, EV_Network, Latitude, Longitude, 
                         Owner_Type_Code, Access_Code, EV_Pricing, EV_Connector) %>%
                  mutate(access_time = case_when(Access_Days_Time == "24 hours daily" ~ "24 hours daily",
                                            Access_Days_Time == "24 hours" ~ "24 hours",
                                            Access_Days_Time == "MON: 24 hours | TUE: 24 hours | WED: 24 hours | THU: 24 hours | FRI: 24 hours | SAT: 24 hours | SUN: 24 hours" ~ "24 hours daily", 
                                            Access_Days_Time == "MO: 12:00am-12:00am; TU: 12:00am-12:00am; WE: 12:00am-12:00am; TH: 12:00am-12:00am; FR: 12:00am-12:00am; SA: 12:00am-12:00am; SU: 12:00am-12:00am" ~ "24 hours daily",
                                            TRUE ~ "Not 24 hours daily")) %>%
                  mutate(ownership = case_when(Owner_Type_Code == "FG" ~ "Federal Government",
                                               Owner_Type_Code == "J" ~ "Joint",
                                               Owner_Type_Code == "LG" ~ "Local Government",
                                               Owner_Type_Code == "P" ~ "aPrivate",
                                               Owner_Type_Code == "SG" ~ "State Government",
                                               Owner_Type_Code == "T" ~ "Utility",
                                               TRUE ~ "Blank",
                                               FALSE ~ "None")) %>%
                  mutate(access_type = case_when(Access_Code == "public" ~ "Public Accessiblity",
                                               Access_Code == "private" ~ "Private Accessibility",
                                               TRUE ~ "zBlank",
                                               FALSE ~ "None")) %>%
                  mutate(freepay = case_when(EV_Pricing == "Free" ~ "Free",
                                             EV_Pricing == "FREE" ~ "Free",
                                             TRUE ~ "Pay",
                                             FALSE ~ "Pay")) %>%
select(Station_Name, Street_Address, City, StateAbb, ZIP, access_time, EV_Network, Latitude, Longitude, ownership, access_type, freepay, EV_Connector)

# Loading ACS Data

us <- unique(fips_codes$state)[1:51]

acs_data <- map_df(us, function(x) {
                  get_acs(geography ="tract",
                          geometry = TRUE,
                          variables = c("B01003_001", "B25001_001", "B25003_001", "B25003_002", 
                                        "B25003_003", "B03002_003", "B03002_004", "B03002_005",
                                        "B03002_006", "B03002_007", "B03002_012", "B08301_001", 
                                        "B08301_003", "B08301_010", "B08301_021", "B19013_001"),
                          output = "wide",
                          state = x,
                          year = 2017)})

colnames(acs_data) <- c("GEOID", "NAME", "Tot_Pop", "Tot_Pop_MOE", "Tot_HU", "Tot_HU_MOE", "Tot_HU_Occ", "Tot_HU_Occ_MOE",
                        "Tot_HU_OwnOcc", "Tot_HU_OwnOcc_MOE", "Tot_HU_RentOcc", "Tot_HU_RentOcc_MOE", "Race_WhiteNH", "Race_WhiteNH_MOE",
                        "Race_BlackNH", "Race_BlackNH_MOE", "Race_IndigenousNH", "Race_IndigenousNH_MOE", "Race_AsianNH", "Race_AsianNH_MOE", 
                        "Race_PacIslNH", "Race_PacIslNH_MOE", "Race_Hispanic", "Race_Hispanic_MOE", "Mode_Total", "Mode_Total_MOE", 
                        "Mode_CarAlone", "Mode_CarAlone_MOE", "Mode_PubTransit", "Mode_PubTransit_MOE", "Mode_WFH", "Mode_WFH_MOE", 
                        "MedInc", "MedInc_MOE", "geometry")

acs_data <- acs_data %>%
  mutate(acs_data, percent_white = (Race_WhiteNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_black = (Race_BlackNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_indig = (Race_IndigenousNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_asian = (Race_AsianNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_pacisl = (Race_PacIslNH / Tot_Pop)*100) %>%
  mutate(acs_data, percent_hispanic = (Race_Hispanic / Tot_Pop)*100) %>%
  mutate(acs_data, percent_caralone = (Mode_CarAlone / Mode_Total)*100) %>%
  mutate(acs_data, percent_pubtransit = (Mode_PubTransit / Mode_Total)*100) %>%
  mutate(acs_data, percent_wfh = (Mode_WFH / Mode_Total)*100)

# Loading Political Variables

poli_vars <- read_csv("Station_Data/political_var.csv") %>%
                  select(states, statename, StateAbb, Gov, StateSen, StateHouse, Leg)

## Merging ACS Variables into EVCS Data

poly_CRS <- st_crs(acs_data)
  evcs_points = st_as_sf(evcs, coords = c("Longitude", "Latitude"), crs = poly_CRS)

# Creating Binary T/F Free EVCS Variable & Joining ACS and Political Variables into EVCS Data

evcs_points <- evcs_points %>%
  select(Station_Name, Street_Address, City, StateAbb, ZIP, access_time, EV_Network, ownership, access_type, freepay, EV_Connector) %>%
  mutate(free = case_when(freepay == "Free" ~ "True",
                         TRUE ~ "False")) %>%
  mutate(public = case_when(access_type == "Public Accessiblity" ~ "True",
                            TRUE ~ "False")) %>%
  mutate(time = case_when(access_time == "Not 24 hours daily" ~ "False",
                           access_time != "Not 24 hours daily" ~ "True")) %>%
  mutate(free_evcs = free == "True" & public == "True" & time == "True") %>%
  st_join(acs_data) %>%
  left_join(poli_vars)
```

```{r}
model1 <- glm(free_evcs ~ ownership + MedInc + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg, 
              data = evcs_points)

summary(model1)
```

```{r log}
model2 <- glm(free_evcs ~ ownership + log(MedInc) + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg, 
              data = evcs_points)

summary(model2)
```


```{r interactions}
model3 <- glm(free_evcs ~ ownership + log(MedInc) + percent_white + percent_black + percent_asian + percent_indig + 
                percent_pacisl + percent_hispanic + percent_caralone + percent_pubtransit + 
                percent_wfh + Gov + Leg, 
                percent_white:Gov +
                percent_white:Leg +
                log(MedInc):Gov +
                log(MedInc):Leg +
                ownership:Gov +
                ownership:Leg,
              data = evcs_points)

summary(model3)
```

## Result Table

```{r results summary}
coef_names <- c("No Ownership Data" = "ownershipBlank", 
                "Federal Ownership" = "ownershipFederal Government", 
                "Joint Ownership" = "ownershipJoint",
                "Local Ownership" = "ownershipLocal Government",
                "State Ownership" = "ownershipState Government",
                "Utility Ownership" = "ownershipUtility",
                "Median Income (log-transformed)" = "log(MedInc)", 
                "Percentage of Population: White (Non-Hispanic)" = "percent_white",
                "Percentage of Population: Black (Non-Hispanic)" = "percent_black",
                "Percentage of Population: Asian (Non-Hispanic)" = "percent_asian",
                "Percentage of Population: Indigenous (Non-Hispanic)" = "percent_indig",
                "Percentage of Population: Pacific Islander (Non-Hispanic)" = "percent_pacisl",
                "Percentage of Population: Hispanic" = "percent_hispanic",
                "Percentage of Workers: Drove Alone" = "percent_caralone",
                "Percentage of Workers: Public Transit" = "percent_pubtransit",
                "Percentage of Workers: Work From Home" = "percent_wfh",
                "Republican Governor" = "GovGOP",
                "Independent Governor" = "GovInd",
                "Republican Legislature" = "LegGOP",
                "Split Legislature" = "LegSplit",
                "Interaction: Percentage White and Republican Governor" = "percent_white:GovGOP",
                "Interaction: Percentage White and Independent Governor" = "percent_white:GovInd",
                "Interaction: Percentage White and Republican Legislature" = "percent_white:LegGOP",
                "Interaction: Percentage White and Split Legislature" = "percent_white:LegSplit",
                "Interaction: Median Income (log) and Republican Governor" = "log(MedInc):GovGOP",
                "Interaction: Median Income (log) and Independent Governor" = "log(MedInc):GovInd",
                "Interaction: Median Income (log) and Republican Legislature" = "log(MedInc):LegGOP",
                "Interaction: Median Income (log) and Split Legislature" = "log(MedInc):LegSplit",
                "Interaction: Blank Ownership and Republic Governor" = "ownershipBlank:GovGOP",
                "Interaction: Federal Ownership and Republic Governor" = "ownershipFederal Government:GovGOP", 
                "Interaction: Joint Ownership and Republic Governor" = "ownershipJoint:GovGOP",
                "Interaction: Local Ownership and Republic Governor" = "ownershipLocal Government:GovGOP",
                "Interaction: State Ownership and Republic Governor" = "ownershipState Government:GovGOP",
                "Interaction: Utility Ownership and Republic Governor" = "ownershipUtility:GovGOP",
                "Interaction: Blank Ownership and Independent Governor" = "ownershipBlank:GovInd",
                "Interaction: Federal Ownership and Independent Governor" = "ownershipFederal Government:GovInd",
                "Interaction: Joint Ownership and Independent Governor" = "ownershipJoint:GovInd",
                "Interaction: Local Ownership and Independent Governor" = "ownershipLocal Government:GovInd",
                "Interaction: State Ownership and Independent Governor" = "ownershipState Government:GovInd",
                "Interaction: Utility Ownership and Independent Governor" = "ownershipUtility:GovInd",
                "Interaction: Blank Ownership and Republican Legislature" = "ownershipBlank:LegGOP",
                "Interaction: Federal Ownership and Republican Legislature" = "ownershipFederal Government:LegGOP",
                "Interaction: Joint Ownership and Republican Legislature" = "ownershipJoint:LegGOP",
                "Interaction: Local Ownership and Republican Legislature" = "ownershipLocal Government:LegGOP",
                "Interaction: State Ownership and Republican Legislature" = "ownershipState Government:LegGOP",
                "Interaction: Utility Ownership and Republican Legislature" = "ownershipUtility:LegGOP",
                "Interaction: Blank Ownership and Split Legislature" = "ownershipBlank:LegSplit",
                "Interaction: Federal Ownership and Split Legislature" = "ownershipFederal Government:LegSplit",
                "Interaction: Local Ownership and Split Legislature" = "ownershipLocal Government:LegSplit",
                "Interaction: State Ownership and Split Legislature" = "ownershipState Government:LegSplit",
                "Interaction: Utility Ownership and Split Legislature" = "ownershipUtility:LegSplit",
                "Constant" = "(Intercept)")

export_summs(model1, model2, model3, coefs = coef_names)
```