---
title: "Station Level"
author: "Carlee Griffeth"
date: "3/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setting Up

## Loading Libraries

*Note: there may be unecessaary libraries in this list; this has become a running list of libraries I've added to try different functions that I've found online so some may not actually be needed.

```{r load libraries, message=FALSE}
library(tidyverse)
library(tidycensus)
library(purrr)
library(survey)
library(srvyr)
library(knitr)
library(jtools)
library(sf)
library(sp)
library(units)
library(nngeo)
library(leaflet)
library(tigris)
library(reshape2)
library(httr)
library(jsonlite)
library(rgdal)
library(maps)
library(mapdata)
library(dplyr)
library(ggplot2)
library(cartogram)
library(ggspatial)
library(ggthemes)
library(rnaturalearth)
library(gtable)
library(descr)
library(nnet)
library(stargazer)
library(foreign)
library(haven)
library(jmv)
library(gmodels)
library(nnet)
library(summarytools)
library("ggthemes")
library("mapproj")
library("ggspatial")

census_api_key("84fd7c10ce8fd8c15d8852fd68abaa8790f1c29d")
options(tigris_use_cache = TRUE)
```

# Loading & Cleaning Data

## EVCS Dataset

Manually downaloaded and read into r.

Electric vehicle charging station data is pulled from the US Department of Energy Alternative Fuels Data Center's Alternative Fueling Station Locator at https://afdc.energy.gov/stations/#/analyze?country=US&fuel=ELEC&ev_levels=all&access=public&access=private

Filtered for download by:
1. Location: United States -- all states/territories
2. Fuel: Electric -- all charger types, all connectors, all networks selected
3. Station: 
    - public and private access; 
    - status: available; 
    - owner: all; 
    - payment: all

```{r loading datasets}
evcs <- read_csv("Station_Data/evcs.csv") %>%
                  select(Station_Name, City, StateAbb, Access_Days_Time, Level_one, Level_two,
                         Level_dc, EV_Network, Latitude, Longitude, Owner_Type_Code, Date_Open, 
                         EV_Connector, Access_Code, EV_Pricing) %>%
                  mutate(access_time = case_when(Access_Days_Time == "24 hours daily" ~ "24 hours daily",
                                            Access_Days_Time == "24 hours" ~ "24 hours daily",
                                            Access_Days_Time == "MON: 24 hours | TUE: 24 hours | WED: 24 hours | THU: 24 hours | FRI: 24 hours | SAT: 24 hours | SUN: 24 hours" ~ "24 hours daily", 
                                            Access_Days_Time == "MO: 12:00am-12:00am; TU: 12:00am-12:00am; WE: 12:00am-12:00am; TH: 12:00am-12:00am; FR: 12:00am-12:00am; SA: 12:00am-12:00am; SU: 12:00am-12:00am" ~ "24 hours daily",
                                            TRUE ~ "Not 24 hours daily")) %>%
                  mutate(level_one = case_when(Level_one > 0 ~ "TRUE")) %>%
                  mutate(level_two = case_when(Level_two > 0 ~ "TRUE")) %>%
                  mutate(level_dc = case_when(Level_dc > 0 ~ "TRUE")) %>%
                  mutate(ownership = case_when(Owner_Type_Code == "FG" ~ "Federal Government",
                                               Owner_Type_Code == "J" ~ "Joint",
                                               Owner_Type_Code == "LG" ~ "Local Government",
                                               Owner_Type_Code == "P" ~ "aPrivate",
                                               Owner_Type_Code == "SG" ~ "State Government",
                                               Owner_Type_Code == "T" ~ "Utility",
                                               EV_Network == "Electrify America" ~ "Electrify America",
                                               EV_Network == "ChargePoint Network" ~ "ChargePoint Network",
                                               TRUE ~ "Other Network",
                                               FALSE ~ "Other Network")) %>%
                    mutate(ownershiptwo = case_when(Owner_Type_Code == "FG" ~ "Public",
                                               Owner_Type_Code == "J" ~ "Other",
                                               Owner_Type_Code == "LG" ~ "Public",
                                               Owner_Type_Code == "P" ~ "Private",
                                               Owner_Type_Code == "SG" ~ "Public",
                                               Owner_Type_Code == "T" ~ "Public",
                                               EV_Network == "Electrify America" ~ "Other",
                                               EV_Network == "ChargePoint Network" ~ "ChargePoint Network",
                                               TRUE ~ "Other",
                                               FALSE ~ "Other")) %>%
                  mutate(access_type = case_when(Access_Code == "public" ~ "Public Accessiblity",
                                               Access_Code == "private" ~ "Private Accessibility",
                                               TRUE ~ "Blank",
                                               FALSE ~ "None")) %>%
                  mutate(freepay = case_when(EV_Pricing == "Free" ~ "Free",
                                             EV_Pricing == "FREE" ~ "Free",
                                             ownership == "ChargePoint Network" ~ "ChargePoint Network",
                                             TRUE ~ "Pay",
                                             FALSE ~ "No Info")) %>%
                  mutate(opendate = case_when(Date_Open <= "43096" ~ "2017 or earlier",
                                             Date_Open >= "43101" ~ "2018 or later",
                                             TRUE ~ "No Date")) %>%
select(Station_Name, City, StateAbb, access_time, level_one, level_two, level_dc, EV_Network, Latitude, Longitude, ownership, ownershiptwo, opendate, EV_Connector, access_type, freepay)

#Creating Dependent Categorical Variable
evcs <- evcs %>%
mutate(dependent = case_when(freepay == "Free" & access_type == "Public Accessiblity" & access_time == "24 hours daily" & ownershiptwo == "Public" ~ "Free & Public",
                             freepay == "Free" & access_type == "Public Accessiblity" & access_time == "24 hours daily" & ownershiptwo == "Private" ~ "aFree & Private",
                             freepay == "Pay" & ownershiptwo == "Public" ~ "Pay & Public",
                             freepay == "Pay" & ownershiptwo == "Private" ~ "Pay & Private",
                             freepay == "ChargePoint Network" ~ "ChargePoint Network",
                             TRUE ~ "Other"))
```

## Loading ACS Data

```{r}
us <- unique(fips_codes$state)[1:51]

us_shape <- map_df(us, function(x) {
                  tracts(state = x, 
                            cb = FALSE, 
                          year = 2017)})

acs_data <- map_df(us, function(x) {
                  get_acs(geography ="tract",
                          geometry = TRUE,
                          variables = c("B01003_001", "B25001_001", "B25003_001", "B25003_002",
                                        "B25003_003", "B03002_003", "B03002_004", "B03002_005",
                                        "B03002_006", "B03002_007", "B03002_012", "B08301_001", 
                                        "B08301_003", "B08301_010", "B08301_021", "B19013_001",
                                        "B25024_001", "B25024_002", "B25024_003"),
                          output = "wide",
                          state = x,
                          year = 2017)})

# Renaming Columns

colnames(acs_data) <- c("TractID", "NAME", "Tot_Pop", "Tot_Pop_MOE", "Tot_HU", "Tot_HU_MOE", "Tot_HU_Occ", "Tot_HU_Occ_MOE",
                        "Tot_HU_OwnOcc", "Tot_HU_OwnOcc_MOE", "Tot_HU_RentOcc", "Tot_HU_RentOcc_MOE", "Race_WhiteNH", "Race_WhiteNH_MOE",
                        "Race_BlackNH", "Race_BlackNH_MOE", "Race_IndigenousNH", "Race_IndigenousNH_MOE", "Race_AsianNH", "Race_AsianNH_MOE", 
                        "Race_PacIslNH", "Race_PacIslNH_MOE", "Race_Hispanic", "Race_Hispanic_MOE", "Mode_Total", "Mode_Total_MOE", 
                        "Mode_CarAlone", "Mode_CarAlone_MOE", "Mode_PubTransit", "Mode_PubTransit_MOE", "Mode_WFH", "Mode_WFH_MOE", 
                        "MedInc", "MedInc_MOE", "Total_Units", "Total_Units_MOE", "Total_Units_Detached", "Total_Units_Detached_MOE", 
                        "Total_Units_Detached1", "Total_Units_Detached1_MOE", "geometry")

```

## Cleaning ACS Data

```{r}
acs_data <- acs_data %>%
  mutate(acs_data, percent_white = (Race_WhiteNH / Tot_Pop)*100) %>%
  mutate(race = case_when(percent_white < "50" ~ "A Majority BIPOC",
                                 percent_white <= "75" & percent_white >= "50" ~ "z25-50% BIPOC",
                                 percent_white > "75" ~ "less than 25% BIPOC",
                                 TRUE ~ "zOther")) %>%
  mutate(acs_data, percent_pubtransit = (Mode_PubTransit / Mode_Total)*100) %>%
  mutate(modeshare = case_when(percent_pubtransit > "50" ~ "A Majority Use Public Transit to Commute",
                                 percent_pubtransit >= "25" & percent_white <= "50" ~ "z25-50% Use Public Transit to Commute",
                                 percent_pubtransit < "25" ~ "less than 25% Use Public Transit to Commute",
                                 TRUE ~ "zOther")) %>%
  mutate(acs_data, percent_units_wo_garage = (((Tot_HU_OwnOcc * 0.19) + (Tot_HU_RentOcc * 0.61)) / Tot_HU_Occ)*100) %>%
  mutate(garage = case_when(percent_units_wo_garage > "50" ~ "A Majority no garage or carport",
                            percent_units_wo_garage < "50" & percent_units_wo_garage > "35" ~ "z35-50% no garage or carport",
                            percent_units_wo_garage < "35" & percent_units_wo_garage > "25" ~ "z25-35% no garage or carport",
                            percent_units_wo_garage < "25" & percent_units_wo_garage > "15" ~ "z15-25% no garage or carport",
                            percent_units_wo_garage < "15" & percent_units_wo_garage > "5" ~ "z5-15% no garage or carport",
                            percent_units_wo_garage < "15" & percent_units_wo_garage > "1" ~ "z1-5% no garage or carport",
                            percent_units_wo_garage < "1" ~ "less than 1% no garage or carport",
                                 TRUE ~ "zOther")) %>%
  mutate(acs_data, percent_multiunit = ((Total_Units - (Total_Units_Detached + Total_Units_Detached1)) / Total_Units)*100) %>%
  mutate(density = case_when(percent_multiunit > "90" ~ "over 90% of housing units have 2+ units",
                            percent_multiunit < "90" & percent_multiunit > "75" ~ "z75-90% of housing units have 2+ units",
                            percent_multiunit < "75" & percent_multiunit > "50" ~ "z50-75% of housing units have 2+ units",
                            percent_multiunit < "50" & percent_multiunit > "25" ~ "a25-50% of housing units have 2+ units",
                            percent_multiunit < "25" & percent_multiunit > "10" ~ "z10-25% of housing units have 2+ units",
                            percent_multiunit < "1" & percent_multiunit > "10" ~ "z1-10% of housing units have 2+ units",
                            percent_multiunit < "1" ~ "less than 1% of housing units have 2+ units",
                                 TRUE ~ "zOther"))
```

## Density Data

```{r setting up density data}
density <- read.csv("Tract_data/densities.csv") %>%
  select(TractID, typeone, typetwo) %>%
  mutate(density1 = case_when(typeone == "A" ~ "Dense",
                              typeone == "B" ~ "Diverse",
                              typeone == "C" ~ "Transient",
                              typeone == "D" ~ "Established",
                              typeone == "E" ~ "Accessible")) %>%
  mutate(density2 = case_when(typetwo == "A" ~ "Rural",
                              typetwo == "B1" ~ "New Development",
                              typetwo == "B2" ~ "Patchwork",
                              typetwo == "B3" ~ "Established Suburb",
                              typetwo == "C1" ~ "Urban Residential",
                              typetwo == "C2" ~ "Old Urban",
                              typetwo == "C3" ~ "Mixed Use")) %>%
select(TractID, density1, density2)
```

## Merging Density Variables into ACS Data

```{r}
tracts <- merge(acs_data, density, by="TractID")
```

## Merging ACS Variables into EVCS Data

```{r}
poly_CRS <- st_crs(tracts)
evcs_points = st_as_sf(evcs, coords = c("Longitude", "Latitude"), crs = poly_CRS)
  
evcs_join <- evcs_points %>%
  st_join(tracts) 
```

## Loading Political Datatset

```{r political data}
poli_vars <- read_csv("Station_Data/political_var.csv") %>%
                  select(states, statename, StateAbb, Gov, StateSen, StateHouse, Leg, Tri_Poli) 
```

## Merging Political Variables into EVCS Data

```{r}
evcs_data <- evcs_join %>%
  left_join(poli_vars)

free_data <- filter(evcs_join, )

write.csv(evcs_data, file = "evcs_data.csv")
```

# Statistics

# Descriptive Stats

```{r descriptive stats}
descriptives(evcs_data, vars = vars(percent_white, MedInc, EV_Network, ownership, ownershiptwo, Tri_Poli, percent_pubtransit, density1, density2), freq = TRUE)

CrossTable(evcs_data$ownership, evcs_data$Tri_Pol)

CrossTable(evcs_data$ownership, evcs_data$density1)

CrossTable(evcs_data$ownership, evcs_data$density2)

CrossTable(evcs_data$ownership, evcs_data$freepay)

CrossTable(evcs_data$freepay, evcs_data$Tri_Pol)

CrossTable(evcs_data$freepay, evcs_data$density1)

CrossTable(evcs_data$freepay, evcs_data$density2)
```

# Regression Models

```{r}
levels(evcs_data$dependent) <- c("Free & Public","aFree & Private",
                                 "Pay & Public","Pay & Private",
                                 "ChargePoint Network", "Other")
OIM <- multinom(dependent ~ 1, data = (evcs_data))
summary(OIM)
```

## Model 1

```{r model 1}
multi_mo1 <- multinom(dependent ~ MedInc + density2 + Tri_Poli + race + modeshare, data = evcs_data, model=TRUE)
summary(multi_mo1)
```

### P-values

```{r model 1 significance ChargePoint Network}
output <- summary(multi_mo1)

print(output)

z <- output$coefficients/output$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

Pclass2 <- rbind(output$coefficients[1,],output$standard.errors[1,],z[1,],p[1,])
rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)
```

```{r model 1 significance Free & Public}
Pclass3 <- rbind(output$coefficients[2,],output$standard.errors[2,],z[2,],p[2,])
rownames(Pclass3) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass3)
```

```{r model 1 significance Other}
Pclass4 <- rbind(output$coefficients[3,],output$standard.errors[3,],z[3,],p[3,])
rownames(Pclass4) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass4)
```

```{r model 1 significance Pay & Private}
Pclass5 <- rbind(output$coefficients[4,],output$standard.errors[4,],z[4,],p[4,])
rownames(Pclass5) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass5)
```

```{r model 1 significance Pay & Public}
Pclass6 <- rbind(output$coefficients[5,],output$standard.errors[5,],z[5,],p[5,])
rownames(Pclass6) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass6)
```

## Model 2

```{r model 2}
multi_mo2 <- multinom(dependent ~ log(MedInc) + density2 + Tri_Poli + race + modeshare, data = evcs_data, model=TRUE)
summary(multi_mo2)
```

## P-values

```{r model 2 significance ChargePoint Network}
output <- summary(multi_mo2)

print(output)

z <- output$coefficients/output$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

Pclass2 <- rbind(output$coefficients[1,],output$standard.errors[1,],z[1,],p[1,])
rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)
```

```{r model 2 significance Free & Public}
Pclass3 <- rbind(output$coefficients[2,],output$standard.errors[2,],z[2,],p[2,])
rownames(Pclass3) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass3)
```

```{r model 2 significance Other}
Pclass4 <- rbind(output$coefficients[3,],output$standard.errors[3,],z[3,],p[3,])
rownames(Pclass4) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass4)
```

```{r model 2 significance Pay & Private}
Pclass5 <- rbind(output$coefficients[4,],output$standard.errors[4,],z[4,],p[4,])
rownames(Pclass5) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass5)
```

```{r model 2 significance Pay & Public}
Pclass6 <- rbind(output$coefficients[5,],output$standard.errors[5,],z[5,],p[5,])
rownames(Pclass6) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass6)
```

```{r model 3}
multi_mo3 <- multinom(dependent ~ MedInc + density2 + Tri_Poli + race + modeshare + MedInc:race, data = evcs_data, model=TRUE)
summary(multi_mo3)
```

## P-values

```{r model 2 significance ChargePoint Network}
output <- summary(multi_mo3)

print(output)

z <- output$coefficients/output$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

Pclass2 <- rbind(output$coefficients[1,],output$standard.errors[1,],z[1,],p[1,])
rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)
```
```{r model 3 significance Free & Public}
Pclass3 <- rbind(output$coefficients[2,],output$standard.errors[2,],z[2,],p[2,])
rownames(Pclass3) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass3)
```

```{r model 3 significance Other}
Pclass4 <- rbind(output$coefficients[3,],output$standard.errors[3,],z[3,],p[3,])
rownames(Pclass4) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass4)
```

```{r model 2 significance Pay & Private}
Pclass5 <- rbind(output$coefficients[4,],output$standard.errors[4,],z[4,],p[4,])
rownames(Pclass5) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass5)
```

```{r model 2 significance Pay & Public}
Pclass6 <- rbind(output$coefficients[5,],output$standard.errors[5,],z[5,],p[5,])
rownames(Pclass6) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass6)
```






### CODE DUMP

multi_mo2 <- multinom(dependent ~ log(MedInc) + density2 + Tri_Poli + race + modeshare, data = evcs_data,model=TRUE)
summary(multi_mo2)

multi_mo3 <- multinom(dependent ~ MedInc + density2 + Tri_Poli + race + modeshare + MedInc:race, data = evcs_data,model=TRUE)
summary(multi_mo3)

mlogit <- nnet::multinom("dependent ~ log(MedInc) + density2 + Tri_Poli + race + modeshare", data = evcs_data)

output <- summary(mlogit)

print(output)

z <- output$coefficients/output$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

exp(coef(output))

Pclass2 <- rbind(output$coefficients[1,],output$standard.errors[1,],z[1,],p[1,])
rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)


mlogit <- nnet::multinom("dependent ~ MedInc + density2 + Tri_Poli + race + modeshare + MedInc:race", data = evcs_data)

output <- summary(mlogit)

print(output)


evcs_data$dependent2 <- relevel(evcs_data$dependent)

multi1 = multinom(dependent ~ MedInc + density1 + Tri_Poli, data = evcs_data)
summary(multi1)

z <- multi1$coefficients/multi1$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

Pclass2 <- rbind(multi1$coefficients[1,],multi1$standard.errors[1,],z[1,],p[1,])

rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)

z <- output$coefficients/output$standard.errors
p <- (1 - pnorm(abs(z), 0, 1))*2

Pclass2 <- rbind(output$coefficients[1,],output$standard.errors[1,],z[1,],p[1,])
rownames(Pclass2) <- c("Coefficient","Std. Errors","z stat","p value")
knitr::kable(Pclass2)
